Stochastic Variance Reduced Policy Gradient

### 2018-01-21 svrpg.tex
Inserted pratical experiment

\section{Experiments}

>>>>

\section{Experiments}
We design our experiments to investigate if:
\begin{enumerate}
\item Algorithm reaches high value of the reward function faster then GPOMDP.
\item Averagely SVRPG maintains the reward function more stable then GPOMDP.
\end{enumerate}

In order to analyze these topics, we evaluate the behavior of rewards function mediated by 10 runs for each experiment.

We decide to use the following models:
\begin{enumerate}
\item \emph{Cart-Pole Balancing} : 4-dimensional state space: cart position x, pole angle $\theta$, the cart velocity $\dot{x}$ , and the pole velocity $\dot{\theta}$; 1-dimensional action space: the horizontal force applied to the cart body. Reward function  is defined as $r(s, a) := 10 - (1 - cos(\theta)) - 10^{-5}\norm[] a^2$. Episodes terminates when $|x|>2.4$ or $|\theta|>0.2$ or the number of time step T is major than 100.
\item \emph{Mujoco Swimmer}: 8-dimensional state space: 3 links velocities ($v_x$ and $v_y$ of center of masses) and 2 actuated joints angles. 2-dimensional action space: the two momentums applied on actuated joints.  Reward function is defined as $r(s, a) := v_x - 10^{-4}\norm[2] a^2$. Episodes terminates when the number of time step T is major than 500.
\item \emph{Mujoco Half Cheetah}: 20-dimensional state space: 9 links and 6 actuated joints angles. 6-dimensional action space: the 6 momentums applied on actuated joints.  Reward function is defined as $r(s, a) := v_x - 0.05\norm[2] a^2$. Episodes terminates when the number of time step T is major than 500.
\end{enumerate}

In all the experiments we face with GPOMDP standard algorithm. GPOMDP uses a number of trajectories per batch that is equal to the number of trajectories used in SVRPO mini-batch size.
In SVRPO we implemented two different Adam parameters: the first one for Snapshot and the second one for sub-iterations.
The stopping condition depends on the maximum number of sub-iterations and on the step size of sub-iteration: in particular we stop if the ratio of step size to number of trajectories used results smaller in sub-iteration than in snapshot.
We fixed the maximum number of trajectories that both the algorithms can use.

All the experiments' parameters are reported in the following table:

\begin{tabular}{ l | c  c  c }	
  & Cart-Pole & Swimmer & Half Cheetah \\
  \hline
  State space dim  & 4 & 8 & 20 \\
  Control space dim & 1 & 2 & 6 \\
  NN Hidden layers & 8 & 32x32 & 32x32 \\
  Learning rate & $10^{-2}$ & $10^{-3}$ & $10^{-3}$ \\
  Snapshot traj & 100 & 100 & 100 \\
  Sub-iter traj & 10 & 10 & 10 \\
  Max sub-iter & 50 & 20 & 20 \\
  Traj lengths& 100 & 500 & 500 \\
  Discount $(\gamma)$& 0.99 & 0.995 & 0.99 \\
  Total traj& 10000 & 10000 & 10000 \\
  \hline  
\end{tabular}
